Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-05-31 Doc/Vrst2013/vrst2013.tex
ADD: abstract
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@580 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\numberofauthors{4}
\author{
% 1st. author
\alignauthor
Tom\'a\v{s} Golembiovsk\'y\\
       \affaddr{Faculty of Informatics}\\
       \affaddr{Masaryk University}\\
       \affaddr{Brno, Czech Republic}\\
       \email{nyoxi@ics.muni.cz}
% 2nd. author
\alignauthor
Igor Peterl\'ik\\
       \affaddr{Institut Hospitalo-Universitaire}\\
       \affaddr{Strasbourg, France}\\
       \email{...} % TODO
% 3rd. author
\alignauthor
Christian Duriez\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{...} % TODO
\and
% 4th. author
\alignauthor
Stephan\'e Cotin\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{...} % TODO
}

@@

\maketitle
\begin{abstract}
  \TODO{}
The accurate mechanical modeling of liver is of a paramount interest in simulation-based operation planning 
and computer-aided per-operative guidance. However, the realistic simulation of liver behaviour is a challenging task, 
since the organ is composed of three constituents: parenchyma, vascularization and Glisson's capsule, each having different mechanical properties. While the 
mechanical influence of vessels on both global and local behaviour of the organ has been measured and modelled previously~\cite{Peterlik2012}, only local 
effects have been studied in the case of Glisson's capsule~\cite{Hollenstein2006,Ahn2010}.

In this paper we introduce what we believe is the first real-time model of liver taking into account all three constituents, each being simulated 
employing a different finite element formulation.
Using the proposed model, we focus on the role of the Glisson's capsule: first, we show that the model is able to reproduce correctly
the local effects of the capsule in so called aspiration test. Second, based on CT image data of porcine abdominal cavity acquired in supine and flank 
positions, we demonstrate 
that the capsule has also a global impact on the mechanical behaviour of the liver in the case when the organ undergoes large deformations.

>>>>

\numberofauthors{4}
\author{
% 1st. author
\alignauthor
Tom\'a\v{s} Golembiovsk\'y\\
       \affaddr{Faculty of Informatics}\\
       \affaddr{Masaryk University}\\
       \affaddr{Brno, Czech Republic}\\
       \email{nyoxi@ics.muni.cz}
% 2nd. author
\alignauthor
Igor Peterl\'ik\\
       \affaddr{Institut Hospitalo-Universitaire}\\
       \affaddr{Strasbourg, France}\\
       \email{Igor.Peterlik@ihu-strasbourg.eu} % TODO
% 3rd. author
\alignauthor
Christian Duriez\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Christian.Duriez@inria.fr} % TODO
\and
% 4th. author
\alignauthor
Stephan\'e Cotin\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Stephane.Cotin@inria.fr} % TODO
}

@@

\maketitle
\begin{abstract}
  \TODO{}
The accurate mechanical modeling of liver is of a paramount interest in simulation-based operation planning 
and computer-aided per-operative guidance. However, the realistic simulation of liver behaviour is a challenging task, 
since the organ is composed of three constituents: parenchyma, vascularization and Glisson's capsule, 
each having different mechanical properties.

While a real-time simulation of vascularized liver has been already described in~\cite{Peterlik2012}, the Glisson's 
capsule has not been included in the modeling. In~\cite{Hollenstein2006,Ahn2010} it is shown that the capsule 
plays an important role mainly in the vicinity of the surgical tools. Therefore, the accuracy of the liver response 
in the vicinity of the surgical tool requires correct modeling of the capsule as a component of the liver model.

The measures perfomed on the capsule show report stiffness which is significanly higher that that of the parenchyma, however, 
the thickness of the membrane does not exceed 100$\mu$m. For this reasons, it is not possible to model the 
capsule with standard volume elements usually employed for the parenchyma. In our approach, we rely of 
corotational membrane elements based on constant-strain formulation, which are coupled mechanically to the underlying 
tetrahedra. We show that using this model we are able to reproduce the experiments reported in~\cite{Hollenstein2006}, 
while maintaining the real-time aspect of the simulation.
